Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-02-16 Paper.tex
link{R__block}

The application of rewards to a block involves raising the balance of the accounts of the beneficiary address of the block and each ommer by a certain amount. We raise the block's beneficiary account by $R_{\mathrm{block}}$; for each ommer, we raise the block's beneficiary by an additional $\frac{1}{32}$ of the block reward and the beneficiary of the ommer gets rewarded depending on the block number.\hypertarget{Omega}{} Formally we define the function $\Omega$:
\begin{eqnarray}
\\ \nonumber
\Omega(B, \boldsymbol{\sigma}) & \equiv & \boldsymbol{\sigma}': \boldsymbol{\sigma}' = \boldsymbol{\sigma} \quad \text{except:} \\
\qquad\boldsymbol{\sigma}'[{\mathbf{B}_{H}}_{\mathrm{c}}]_{\mathrm{b}} & = & \boldsymbol{\sigma}[{\mathbf{B}_{H}}_{\mathrm{c}}]_{\mathrm{b}} + (1 + \frac{\lVert \mathbf{B}_{\mathbf{U}}\rVert}{32})R_{\mathrm{block}} \\
\qquad\forall_{\mathbf{U} \in \mathbf{B}_{\mathbf{U}}}: \\ \nonumber
\boldsymbol{\sigma}'[\mathbf{U}_{\mathrm{c}}] & = & \begin{cases}
\varnothing &\text{if}\ \boldsymbol{\sigma}[\mathbf{U}_{\mathrm{c}}] = \varnothing\ \wedge\ R = 0 \\
\mathbf{a}' &\text{otherwise}
\end{cases} \\
\mathbf{a}' &\equiv& (\boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{n}}, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{b}} + R, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathbf{s}}, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{c}}) \\
R & \equiv & (1 + \frac{1}{8} (U_{\mathrm{i}} - {B_{H}}_{\mathrm{i}})) R_{\mathrm{block}}
\end{eqnarray}

@@

\hypertarget{block_reward_R__block}{}We define the block reward as 3 Ether:
\begin{equation}
\text{Let} \quad R_{\mathrm{block}} = 3 \times 10^{18}
\end{equation}

>>>>

The application of rewards to a block involves raising the balance of the accounts of the beneficiary address of the block and each ommer by a certain amount. We raise the block's beneficiary account by \hyperlink{$R_{\mathrm{block}}$}; for each ommer, we raise the block's beneficiary by an additional $\frac{1}{32}$ of the block reward and the beneficiary of the ommer gets rewarded depending on the block number.\hypertarget{Omega}{} Formally we define the function $\Omega$:
\begin{eqnarray}
\\ \nonumber
\Omega(B, \boldsymbol{\sigma}) & \equiv & \boldsymbol{\sigma}': \boldsymbol{\sigma}' = \boldsymbol{\sigma} \quad \text{except:} \\
\qquad\boldsymbol{\sigma}'[{\mathbf{B}_{H}}_{\mathrm{c}}]_{\mathrm{b}} & = & \boldsymbol{\sigma}[{\mathbf{B}_{H}}_{\mathrm{c}}]_{\mathrm{b}} + (1 + \frac{\lVert \mathbf{B}_{\mathbf{U}}\rVert}{32})R_{\mathrm{block}} \\
\qquad\forall_{\mathbf{U} \in \mathbf{B}_{\mathbf{U}}}: \\ \nonumber
\boldsymbol{\sigma}'[\mathbf{U}_{\mathrm{c}}] & = & \begin{cases}
\varnothing &\text{if}\ \boldsymbol{\sigma}[\mathbf{U}_{\mathrm{c}}] = \varnothing\ \wedge\ R = 0 \\
\mathbf{a}' &\text{otherwise}
\end{cases} \\
\mathbf{a}' &\equiv& (\boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{n}}, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{b}} + R, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathbf{s}}, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{c}}) \\
R & \equiv & (1 + \frac{1}{8} (U_{\mathrm{i}} - {B_{H}}_{\mathrm{i}})) R_{\mathrm{block}}
\end{eqnarray}

@@

\hypertarget{block_reward_R__block}{}\linkdest{R__block}We define the block reward as 3 Ether:
\begin{equation}
\text{Let} \quad R_{\mathrm{block}} = 3 \times 10^{18}
\end{equation}
